\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{center}
    \href{https://zaheer-sidik.github.io/personal-website/}
         {\textbf{\Huge \scshape Zaheer Abbas Sidik}} \\[0.3em]
    \small 
    +44 7508 662381 $|$
    \href{mailto:zaheersidik11@gmail.com}{\underline{zaheersidik11@gmail.com}} $|$
    \href{https://www.linkedin.com/in/zaheer-sidik}{\underline{linkedin.com/in/zaheer-sidik}}
\end{center}




%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {University of Oxford}{Keble College, Oxford}
      {MEng in Engineering Science: Currently ranked in top 13\% of cohort}{Sept. 2022 -- Present}
      \begin{itemize}[noitemsep]
      \item Preliminary Examinations: Distinction
      \item Second Year Examinations: First Class
      \item Third Year Examinations: First Class
      \end{itemize}
  \resumeSubHeadingListEnd
  \vspace{-0.5cm}
  
  \resumeSubHeadingListStart
    \resumeSubheading
      {Parmiter's High School}{Garston, Hertfordshire}
      {A - Levels:}{Sept. 2020 -- Jun. 2022}
      \begin{itemize}
          \item Chemistry, Physics, Maths, Further Maths: A*
      \end{itemize}
      \resumeSubSubheading{GCSEs:}{Sept. 2015 -- Jun. 2020}
      \begin{itemize}[noitemsep, topsep=0pt]
        \item Chemistry, Physics, Biology, Maths, Geography: 9
        \item Electronics, Economics, Spanish, English Literature: 8
        \item English Language: 7
      \end{itemize}
  \resumeSubHeadingListEnd

\section{Awards}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Keble College}{University of Oxford}
      {College Scholarship}{2025 -- 2026}
      \resumeItemListStart
        \resumeItem{Awarded the College Scholarship for outstanding academic performance in third-year examinations, achieving a First Class grade.}
      \resumeItemListEnd

    \resumeSubheading
      {Keble College}{University of Oxford}
      {College Scholarship}{2024 -- 2025}
      \resumeItemListStart
        \resumeItem{Awarded the College Scholarship for outstanding academic performance in second-year examinations, achieving a First Class grade.}
      \resumeItemListEnd

    \resumeSubheading
      {Keble College}{University of Oxford}
      {College Scholarship}{2023 -- 2024}
      \resumeItemListStart
        \resumeItem{Awarded the College Scholarship for exceptional performance in preliminary examinations, achieving a Distinction.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

  
\section{Research Experience and Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://zaheer-sidik.github.io/Sprint-Time-Predictor/}{Sprint Training Time Predictor}}{}
      {Personal Project}{}
      \resumeItemListStart
        \resumeItem{Developed a machine learning model to predict sprint training times based on historical performance data.}
        \resumeItem{Implemented data visualization features to track progress and analyze training patterns.}
        \resumeItem{Deployed the application as an interactive web tool for athletes and coaches.}
      \resumeItemListEnd

  \resumeSubheading
      {AVEVA}{July 2025 -- Aug. 2025}
      {Software Developer - Intern}{Cambridge Science Park}
      \resumeItemListStart
        \resumeItem{Implemented a language server within the PML (Programmable Macro Language) VSCode extension and implemented features such as "Go to definition".}
        \resumeItem{Resolved coverity issues using Polaris.}
        \resumeItem{Implemented API functionality to allow for a drop down combobox in a RUR (Release Update Request) form.}
      \resumeItemListEnd

      \resumeSubheading
      {University of Oxford}{Oct. 2024 -- June 2025}
      {Cultured Meat Production - Group Research Project}{Department of Engineering Science, Oxford}
      \resumeItemListStart
        \resumeItem{Led the design of the differentiation stage, focusing on bioreactor design for myogenesis and adipogenesis.}
        \resumeItem{Modelled heat generation within bioreactors using ASPEN Plus to inform reactor wall thickness and jacket sizing.}
        \resumeItem{Developed the overall material and energy balance for the plant and used it to estimate CapEx and OpEx for financial analysis.}
        \resumeItem{Performed an optimisation study for plant location and supply chain strategy, assessing supplier networks and sensitivity to disruption.}
      \resumeItemListEnd

      \resumeSubheading
      {University of Oxford}{Oct. 2024 -- Jan. 2024}
      {Sustainable Computing - Research Project}{Department of Engineering Science, Oxford}
      \resumeItemListStart
        \resumeItem{Developed models to predict UK carbon intensity on hourly, daily, monthly, and yearly timescales using Facebook's Prophet and LightGBM.}
        \resumeItem{Analysed national carbon intensity data using quanitative methods to determine optimal periods for running computationally intensive tasks to minimise emissions.}
        \resumeItem{Characterised the power consumption behaviour of two laptop architectures under machine learning workloads using PowerTOP.}
        \resumeItem{Produced findings to guide sustainable computing practices through data-driven decision-making.}
      \resumeItemListEnd




    \resumeSubheading
      {University of Oxford}{June 2024 -- Aug. 2024}
      {CFD Analyst - Intern}{Engineering Department, Oxford}
      \resumeItemListStart
        \resumeItem{Simulated multiphase flow of Liquid Nitrogen over heatsinks in Power Electronics Applications to model the effects of changing geometry on transistor temperature using Ansys Fluent.}
        \resumeItem{Generated geometry using Solidworks and Ansys SpaceClaim and analysed results using CFD-Post.}
        \resumeItem{Utilised command line applications to generate rgp files for the gas properties.}
      \resumeItemListEnd
      

    
  \resumeSubHeadingListEnd

\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {ZASTutoring}{Sept. 2021 - Present}
      {Tutor and Founder}{Online}
      \resumeItemListStart
        \resumeItem{Started my own tutoring company to provide affordable high-quality lessons from students at the University of Oxford.}
        \resumeItem{Employed 2 more tutors to cope with additional demand.}
        \resumeItem{Developed the skill of teaching and managing a business through social media.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Ryman}{Sept. 2021 -- June. 2022}
      {Sales Assistant}{Edgware, London}
      \resumeItemListStart
        \resumeItem{Worked a part time job during my final years of high school to give myself experience in a working environment.}
        \resumeItem{Developed communication and time management skills.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd




\section{Volunteering}
  \resumeSubHeadingListStart

    \resumeSubheading
      {OUABSoc}{May 2025 -- May 2026}
      {President}{Oxford University}
      \resumeItemListStart
        \resumeItem{Led and organised weekly events.}
        \resumeItem{Worked as part of a team to hold larger events open to external guests.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------Skill and Interests-----------
\section{Skills \& Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \vspace{1mm}
     \textbf{Skills: }{Ansys Fluent, Solidworks, VSCode Language Extensions} \\
     \vspace{1mm}
     \textbf{Programming Languages: }{MATLAB, Python, C++, Typescript} \\
     \vspace{1mm}
     \textbf{Interests: }{Athletics, Tech, Sustainability, Computational Modelling, Chemical Engineering} \\
     \textbf{Languages: }{English, Arabic [Limited Proficiency]}
     \vspace{1mm}

    }}
 \end{itemize}


\end{document}